Efficient simulation of individual-based population models

### 2024-03-27 article.qmd
insurance mini update

**Death events** A baseline age and time specific death rate is first
calibrated on "England and Wales (EW)" males mortality historic
data[^1], and projected for 30 years using the Lee-Carter model with the
package `StMoMo` (see [@stmomo]). The forecasted baseline death
intensity is denoted by $d(t,a)$, defined by:
$$
d(t,a) = \sum_{k=0}^{29}\mathbf{1}_{\{k\leq t < k+1\}} d_k(a), \quad \forall \; t\in [0,30] \text{ and } a \in [65, a_{\max}],
$$ {#eq-insurance-baseline}
with $d_k(a)$ the point estimate of the forecasted mortality rate for
age $a$ and year $k$.\
Individuals in risk class 1 are assumed to have mortality rates that are
20% higher than the baseline mortality (for instance, the risk class
could refer to smokers), while individuals in risk class 2 are assumed
to have mortality rates that are 20% lower than the baseline (non
smokers). The death intensity of an individual $I= (\tau_b, \infty, x)$,
of age $a(I,t) = t - \tau_b$ at time $t$ and in risk class
$x \in \{1, 2\}$ is thus the function $$
\lambda^d(t,I) = \alpha_x d(t,a(I,t)), \quad \alpha_1 = 1.2, \quad \alpha_2 = 0.8.
$$
In particular, the death intensity verifies @cnj-intensity2 since:
$$
\lambda^d(t,I) \leq \bar d : = \alpha_1 \sup_{t \in [0,30]} d(t,a_{\max}).
$$ {#eq-insurance-bound-deathrates}

@@

dim(population_alive(sim_out$population,t = 30))

sim_out$logs[["duration_ns"]]/1e9

sim_out$logs[["effective_events"]] / sim_out$logs[["proposed_events"]]

>>>>

**Death events** A baseline age and time specific death rate is first
calibrated on "England and Wales (EW)" males mortality historic
data (source: Human Mortality Database <https://www.mortality.org/>), and projected for 30 years using the Lee-Carter model with the
package `StMoMo` (see [@stmomo]). The forecasted baseline death
intensity is denoted by $d(t,a)$, defined by:
$$
d(t,a) = \sum_{k=0}^{29}\mathbf{1}_{\{k\leq t < k+1\}} d_k(a), \quad \forall \; t\in [0,30] \text{ and } a \in [65, a_{\max}],
$$ {#eq-insurance-baseline}
with $d_k(a)$ the point estimate of the forecasted mortality rate for
age $a$ and year $k$.\
Individuals in risk class 1 are assumed to have mortality rates that are
20% higher than the baseline mortality (for instance, the risk class
could refer to smokers), while individuals in risk class 2 are assumed
to have mortality rates that are 20% lower than the baseline (non
smokers). The death intensity of an individual $I= (\tau_b, \infty, x)$,
of age $a(I,t) = t - \tau_b$ at time $t$ and in risk class
$x \in \{1, 2\}$ is thus the function $$
\lambda^d(t,I) = \alpha_x d(t,a(I,t)), \quad \alpha_1 = 1.2, \quad \alpha_2 = 0.8.
$$
In particular, the death intensity verifies @cnj-intensity2 since:
$$
\lambda^d(t,I) \leq \bar d : = \alpha_1 \sup_{t \in [0,30]} d(t,a_{\max}).
$$ {#eq-insurance-bound-deathrates}

@@

print(paste("Number of alive individuals in the population at final time T=30 : " ,dim(population_alive(sim_out$population,t = 30))[1], sep=""))

print(paste("Execution time : ", sim_out$logs[["duration_ns"]]/1e9, "s", sep=""))

print(paste("Proportion of effective events and proposed events : ", sim_out$logs[["effective_events"]] / sim_out$logs[["proposed_events"]], sep=""))
